Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-09 papers/marlowe2019/paper.tex
Draft conclusions written.

Conclusions (draft)
\begin{itemize}
\item
Using a DSL means that we can d o much better with analysis and proof than a general purpose language.
\item
Defining the language by means of an executable reference semantics means that we can, as well as directly executing this semantics, generate an on-chain interpreter for it and simulate it in browser using the Haskell-like languages Plutus and PrueScript. This is made particularly straightforward by working in the subset of Haskell that directly corresponds to what translates directly into these languages.
\item

\end{itemize}

>>>>

Conclusions (draft)
\begin{itemize}
\item
Using a DSL means that we can do much better with analysis and proof than a general purpose language: so much that we can incorporate the analysis in the development environment.
\item
Defining the language by means of an executable reference semantics means that we can, as well as directly executing this semantics, generate an on-chain interpreter for it and simulate it in browser using the Haskell-like languages Plutus and PrueScript. This is made particularly straightforward by working in the subset of Haskell that directly corresponds to what translates directly into these languages.
\item
Different development modes: visual and Haskell-aided.
\item
Something about ACTUS?
\item \ldots
\end{itemize}

\medskip\noindent
Future Work (draft)
\begin{itemize}
\item Tokenising and securitising contracts.
\item Other implementations e.g. Ethereum
\item Multi-currency
\item Launching on Cardano blockchain itself 
\item \ldots
\end{itemize}
